Usage metrics

### 2020-12-15 analysis/Attic/analysis_stable.Rmd

# Corpus

TODO

@@

### String size

```{r}
eval_calls %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length, weight = nb_ev_calls), na.rm = TRUE, binwidth=1) +
  scale_x_log10() +  scale_y_sqrt()
```

If we remove the outliers:
```{r}
eval_calls %>% filter(expr_expression_length < 25000) %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length, weight = nb_ev_calls), na.rm = TRUE, binwidth=2)  + scale_x_sqrt() +  scale_y_sqrt() 
```

What about the code size of expressions that seem to be generated?
An approximation of *generated* will be no `srcref` and not in `base`.

```{r code_size_srcref}
eval_calls %>% filter(is.na(eval_call_srcref), caller_package != "base") %>% ggplot() +
  geom_histogram(aes(x = expr_expression_length, weight = nb_ev_calls), na.rm = TRUE, binwidth=1) + scale_x_sqrt() + scale_y_sqrt()
```

And the average size per package:
```{r average_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(average_expr_size = mean(expr_expression_length, na.rm = TRUE)) %>% arrange(desc(average_expr_size))
```

If we look at the maxima, the largest ones are in *base*:
```{r max_size_package}
eval_calls %>% group_by(caller_package) %>% summarize(max_expr_size = max(expr_expression_length, na.rm = TRUE)) %>% arrange(desc(max_expr_size))
```

@@

classified_envir_packages %>% select(env_class, eval_call_expression, eval_call_srcref, caller_expression, n) %>% distinct() %>% datatable()
```

>>>>

@@

@@

classified_envir_packages %>% select(env_class, eval_call_expression, eval_call_srcref, caller_expression, caller_srcref, n) %>% distinct() %>% datatable()
```

And per call sites?

```{r frequent_env_per_call_sites}
classified_envir_prop_core_call_sites <- classified_envir %>% 
  filter(dataset == "core") %>%
  group_by(env_class) %>% 
  summarize(n = vec_unique_count(eval_call_srcref)) %>%
  arrange(desc(n)) %>% 
  mutate(proportion = n / sum(n))

classified_envir_prop_packages_call_sites <- classified_envir %>% 
  filter(dataset == "packages") %>%
  group_by(env_class) %>% 
  summarize(n = vec_unique_count(eval_call_srcref)) %>%
  arrange(desc(n)) %>% 
  mutate(proportion = n / sum(n))

### 2020-12-15 analysis/corpus.Rmd

corpus %>%
  mutate(
    outlier=evals_dyn > PACKAGE_EVALS_DYN_OUTLIER,# | package_r_code > PACKAGE_SIZE_OUTLIER,
    label=ifelse(outlier, package, NA),
    code_size=cut(package_r_code, size_bins, labels=size_bins_lasb, include.lowest=TRUE)
  ) %>%
  ggplot(
    aes(
      x=coverage_expr, 
#      y=funs_with_eval,
      y=evals_dyn,
      label=label,
      size=code_size
    )
  ) +
  geom_point(alpha=.4) +
  geom_text(size=3, check_overlap = T, vjust=-1.5, na.rm = TRUE) + 
  geom_hline(aes(yintercept=funs_with_eval_mean), linetype="dashed", color="red", size=0.2) +
  geom_vline(aes(xintercept=coverage_mean), linetype="dashed", color="red", size=0.2) +
  scale_x_continuous(labels = scales::percent) + 
  scale_y_continuous(trans=scales::pseudo_log_trans(), breaks=c(0, 1, 2, 5, 10, 20, 50, 100, 200, 500)) +
  scale_size_discrete(range = c(1, 6)) +
  theme(
    legend.position=c(0.2, 0.85),
    legend.box="horizontal",
    legend.box.background = element_rect(fill="white", size=0.1)
  ) +
  labs(
    x="Code coverage", 
    y="Number of eval call sites", 
    size="Lines of R code",
    linetype=""
  ) +
  guides(
    size=guide_legend(order=1),
    color=FALSE,
    linetype=FALSE
  )

>>>>

corpus %>%
  mutate(
    outlier=evals_dyn > PACKAGE_EVALS_DYN_OUTLIER,# | package_r_code > PACKAGE_SIZE_OUTLIER,
    label=ifelse(outlier, package, NA),
    code_size=cut(package_r_code, size_bins, labels=size_bins_lasb, include.lowest=TRUE)
  ) %>%
  ggplot(
    aes(
      x=coverage_expr, 
#      y=funs_with_eval,
      y=evals_dyn,
      label=label,
      size=code_size
    )
  ) +
  geom_point(alpha=.4) +
  geom_text(size=3, check_overlap = T, vjust=-1.5, na.rm = TRUE) + 
  geom_hline(aes(yintercept=funs_with_eval_mean), linetype="dashed", color="red", size=0.2) +
  geom_vline(aes(xintercept=coverage_mean), linetype="dashed", color="red", size=0.2) +
  scale_x_continuous(labels = scales::percent) + 
  scale_y_continuous(trans=scales::pseudo_log_trans(), breaks=c(0, 1, 2, 5, 10, 20, 50, 100, 200, 500)) +
  scale_size_discrete(range = c(1, 6)) +
  theme(
    legend.position=c(0.15, 0.73),
    legend.box="horizontal",
    legend.box.background = element_rect(fill="white", size=0.1)
  ) +
  labs(
    x="Code coverage", 
    y="Number of eval call sites", 
    size="Lines of R code",
    linetype=""
  ) +
  guides(
    size=guide_legend(order=1),
    color=FALSE,
    linetype=FALSE
  ) +
  expand_limits(y = 300)

### 2020-12-15 analysis/environments.Rmd

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) { # record the current time before each chunk
      now <<- Sys.time()
    } else { # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res, units(res))
}}}))

knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center",
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

@@

```{r}
eval_calls_arg_caller %>% count(envir_from_arg, wt=nb_ev_calls, sort = TRUE) %>% knitr::kable()
```

>>>>

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) { # record the current time before each chunk
      now <<- Sys.time()
    } else { # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res, units(res))
    }
  }
}))

knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  fig.retina = 2,
  fig.width = 10,
  cache.lazy = FALSE
)

@@

```{r}
eval_calls_arg_caller %>%
  count(envir_from_arg, wt = nb_ev_calls, sort = TRUE) %>%
  knitr::kable()
```

### 2020-12-15 analysis/usage.Rmd

@@

@@

>>>>

```{r eval-calls-summary}

eval_calls_table <- E %>% 
  count(ev_package, wt=duplicates, sort = TRUE)

breaks <- c(0, 10, 100, 1000, 10000, 100000, 1000000, 10000000, 100000000)

group_tags <- cut(eval_calls_table$n,
                  breaks = breaks,
                  include.lowest = TRUE)

ev_summary <- summary(group_tags)

r("bin1", ev_summary[[1]])
r("bin2", ev_summary[[2]])
r("bin3", ev_summary[[3]])
r("bin4", ev_summary[[4]])
r("bin5", ev_summary[[5]])
r("bin6", ev_summary[[6]])
r("bin7", ev_summary[[7]])
r("bin8", ev_summary[[8]])
```

@@

And now, by `eval` variant:

```{r exercised-call-site-per-variant}

static_eval <- P %>% filter(call_fun_name == "eval") %>% nrow()
static_evalq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
static_eval.parent <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
static_local <- P %>% filter(call_fun_name == "local") %>% nrow()

sites_per_variant <- E %>% # src_ref indicates where the call originates from.
  group_by(ev_variant) %>% 
  summarize( n = n_distinct(src_ref)) # This the number of distinct sites

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval") %>% .$n
trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq") %>% .$n
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") %>% .$n
trig_local <- sites_per_variant %>% filter(ev_variant == "local") %>% .$n

r("static eval", static_eval)
r("static evalq", static_evalq)
r("static eval.parent", static_eval.parent)
r("static local", static_local)

r("triggered eval", trig_eval)
r("triggered evalq", trig_evalq)
r("triggered eval.parent", trig_eval.parent)
r("triggered local", trig_local)

r("eval percent call site", ratio(trig_eval, static_eval))
r("evalq percent call site", ratio(trig_evalq, static_evalq))
r("eval.parent percent call site", ratio(trig_eval.parent, static_eval.parent))
r("local percent call site", ratio(trig_local, static_local))
```

@@

```{r}
eval_call_triggered <- E %>% 
  group_by(src_ref) %>%
  summarize(n_runs = n_distinct(file), n = sum(duplicates), average = n / n_runs) %>%
  arrange(desc(average))
```
